---
title: "Marcus_Ar_Bast_Rappot"
format: html
---
# 1) Dataförståelse
source("../scripts/")
```{r}

source("../scripts/load_data.R")
source("../scripts/utility.R")

df_raw <- load_data("../data/insurance_costs.csv")
look_at_data(df_raw,skip_col = "customer_id")

```

The Dataset consists of 1100 rows and 14 columns.

There are only char and dbl data types and  customer_id has data type char thanks to "C100000" having
a C in front.

Missing Values:

- bmi: 28 missing values.
- exercise_level: 22 missing values.
- annual_checkups: 20 missing values.

Inconsistencies in the date:

inconsistent capitalization:

- region: "north" and "North", "south" and "Shouth"
- smoker: "yes" and "Yes"
- plan_type: "standard" and "Standard", "premium" and "Premium"

#2) Datastädning och förberedelse

```{r}
source("../scripts/clean_data.R")
df_clean <- clean_data(df_raw)
look_at_data(df_clean)
print(unique(df_clean$prior_claims))
```

Removed the C from customer_id.

Made new Column:

- age_group age < 30 =  "under 30", age < 45 = "30-44", age < 60 = "45-59", the rest = "60 and above"

Filled missing inside Columns:

- exercise_level by taking the median as something like exercise can easily be screwed both high and low.
- annual_checkups by taking the median for the same reason as exercise_level.
- bmi by grouping the bmi by sex, age_group,exercise_level and taking the median value.

Change datatypes:

From char to factor:

- sex
- region
- exercise_level
- plan_type

From dbl to int:

- age
- children
- prior_accidents      
- prior_claims   
- annual_checkups           

From char to logic:

- smoker
- chronic_condition    




```{r}
source("../scripts/add_column.R")
df_add_column <- bmi_category(df_clean)
df_add_column <- health_risk_level(df_add_column)
look_at_data(df_add_column)
```





Example of an comment. 
Here is the place i will write my comments and the report of 
- syfte
- metod
- resultat
- regressionsanalys
- slutsatser
- begränsningar







```{r}

ggplot(df_clean)

```






