---
title: "Marcus_Ar_Bast_Rappot"
format: html
---
# 1) Dataförståelse
source("../scripts/")
```{r}

source("../scripts/load_data.R")
source("../scripts/utility.R")

df_raw <- load_data("../data/insurance_costs.csv")
look_at_data(df_raw,skip_col = "customer_id")

```

The Dataset consists of 1100 rows and 14 columns.

There are only char and dbl data types and  customer_id has data type char thanks to "C100000" having
a C in front.

Missing Values:

- bmi: 28 missing values.
- exercise_level: 22 missing values.
- annual_checkups: 20 missing values.

Inconsistencies in the date:

inconsistent capitalization:

- region: "north" and "North", "south" and "Shouth"
- smoker: "yes" and "Yes"
- plan_type: "standard" and "Standard", "premium" and "Premium"

#2) Datastädning och förberedelse

```{r}
source("../scripts/clean_data.R")
df_clean <- clean_data(df_raw)
look_at_data(df_clean)
print(unique(df_clean$prior_claims))
```
Made a new column age_group to put costumers into age groups and to use it together with sex and exercise_level to fill in the bmi by taking the median of their age_group and exercise_level and sex and filling the NA of bmi. filled the NA of both annual_checkups and exercise_level by their median as they are prone to screwed data median fits better then mean.

Turned the relative char column variables into factor variables and change dbl variables into int variables. 

Removed the C from customer_id.


```{r}
source("../scripts/add_column.R")
df_add_column <- bmi_category(df_clean)
df_add_column <- health_risk_level(df_add_column)
look_at_data(df_add_column)
```





Example of an comment. 
Here is the place i will write my comments and the report of 
- syfte
- metod
- resultat
- regressionsanalys
- slutsatser
- begränsningar







```{r}

ggplot(df_clean)

```






