---
title: "Marcus_Ar_Bast_Rappot"
format: html
---

source("../scripts/")
```{r}

source("../scripts/load_data.R")

source("../scripts/utility.R")

df_raw <- load_data("../data/insurance_costs.csv")
look_at_data(df_raw,skip_col = "customer_id")

```
# 1) Dataförståelse

The Dataset consists of 1100 rows and 14 columns.

There are only char and dbl data types and  customer_id has data type char thanks to "C100000" having
a C in front.

Missing Values:

- bmi: 28 missing values.
- exercise_level: 22 missing values.
- annual_checkups: 20 missing values.

Inconsistencies in the date:

inconsistent capitalization:

- region: "north" and "North", "south" and "Shouth"
- smoker: "yes" and "Yes"
- plan_type: "standard" and "Standard", "premium" and "Premium"


```{r}
source("../scripts/Marcus_Ar_Bast_Script1.R")
df <- load_data("../data/insurance_costs.csv")
print_unique_chars_only(df)
df_clean <- clean_data(df)
print_unique_chars_only(df_clean)
```

```{r}
source("../scripts/clean_data.R")
df_clean <- clean_data(df_raw)
print_unique_chars_only_v2(df_clean)
look_at_data(df_clean)
print(unique(df_clean$prior_claims))
```





Example of an comment. 
Here is the place i will write my comments and the report of 
- syfte
- metod
- resultat
- regressionsanalys
- slutsatser
- begränsningar







```{r}

ggplot(df_clean)

```






